---
title: "Analysis - Hormones"
author: "Wanitchaya Poonpatanapricha"
output: github_document
---

```{r setup, include = F}
# global setting
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
options(warn = -1)

# load libraries
library(tidyverse)
library(ggplot2)
library(ggpmisc)
library(rcompanion)
library(knitr)
library(broom)
# setting theme for ggplot
theme_set(theme_minimal())
theme_update(text = element_text(family = "Times"))
```

```{r}
# Functions to be used

## ploting the mean of hormone concentration with 95% confidence interval
## over 3 sessions, grouped by condition
## input: dataframe that contain only the hormone in interest
##        (either cortisol or testosterone)
plot_repeated_meas <- function(hormone) {
  # Calculate needed statistic
  Sum = groupwiseMean(
    Conc ~ tsst + session,
    data   = hormone,
    conf   = 0.95,
    traditional = FALSE,
    percentile  = TRUE
  )
  # plot
  ggplot(Sum, aes(session, Mean, color = tsst)) +
    # 95% Confidence interval
    geom_errorbar(
      aes(ymin = Percentile.lower,
          ymax = Percentile.upper),
      width = .2,
      size = 0.7,
      position = position_dodge(.2)
    ) +
    geom_point(shape = 15,
               size = 4,
               position = position_dodge(.2)) +
    labs(title = "",
         y = "Concentration",
         x = "Session") + 
    scale_color_discrete(name = "")
}

plot_all <- function(hormone) {
  # Calculate needed statistic
  Sum = groupwiseMean(
    Conc ~ session,
    data   = hormone,
    conf   = 0.95,
    traditional = FALSE,
    percentile  = TRUE
  )
  # plot
  ggplot(Sum, aes(session, Mean)) +
    # 95% Confidence interval
    geom_errorbar(
      aes(ymin = Percentile.lower,
          ymax = Percentile.upper),
      width = .2,
      size = 0.7,
      position = position_dodge(.2)
    ) +
    geom_point(shape = 15,
               size = 4,
               position = position_dodge(.2)) +
    labs(title = "",
         y = "Concentration",
         x = "Session")
}
```

```{r raw_data,warning = FALSE, message = FALSE}
## load the data

# hormone concentration data
hormone <- read_csv("../data/2018 Assay Data - Sheet1.csv")

# the information of each subject
subject <-
  read_csv(
    "../data/Participant Information _ Condition Spreadsheet - Participants.csv",
    col_names = TRUE,
    col_types = cols()
  )

```

```{r tidying, cache = TRUE, dependson = "raw_data"}
## Tidying and combining data

# Tidying hormone data
hormone <- hormone %>%
  select(-"Participant #")

# Tidying subject data
subject <- subject %>%
  slice(2:157) %>%
  select("Participant #","Participant ID", "Condition # (1-8)", 
         "Gender", "TSST/Control Condition", "Judges Sex") %>%
  mutate(Gender = ifelse(Gender == "F","Female","Male"))
colnames(subject) <- c("number","ID","condition","gender","tsst","judge_sex")
subject <- mutate(subject,judge_sex = ifelse(judge_sex == "F","Female","Male"))

# create a combined dataframe
# each observation = each subject in each hormone in each session
relation <- full_join(subject, hormone, by = c("ID" = "Participant ID")) %>%
  select(number, everything(), -Cort_A_S1_Conc, -Cort_B_S1_Conc, -Cort_C_S1_Conc, 
         -Cort_A_S2_Conc, -Cort_B_S2_Conc, -Cort_C_S2_Conc, -Testo_A_S1_Conc, 
         -Testo_B_S1_Conc, -Testo_C_S1_Conc, -Testo_A_S2_Conc, -Testo_B_S2_Conc, -Testo_C_S2_Conc) %>%
  # create a column contain difference of concentration between session
  mutate(Diff_Cort_B_A = Cort_B_Conc - Cort_A_Conc,
         Diff_Cort_C_B = Cort_C_Conc - Cort_B_Conc,
         Diff_Testo_B_A = Testo_B_Conc - Testo_A_Conc,
         Diff_Testo_C_B = Testo_C_Conc - Testo_B_Conc) %>%
  unite("Cort", c(Cort_A_Conc, Cort_A_Std_Dev, "CV_(%)_Cort_A",
                  Cort_B_Conc, Cort_B_Std_Dev, "CV_(%)_Cort_B",
                  Cort_C_Conc, Cort_C_Std_Dev, "CV_(%)_Cort_C",
                  Diff_Cort_B_A, Diff_Cort_C_B)) %>%
  unite("Testo", c(Testo_A_Conc, Testo_A_Std_Dev, "CV_(%)_Testo_A",
                  Testo_B_Conc, Testo_B_Std_Dev, "CV_(%)_Testo_B",
                  Testo_C_Conc, Testo_C_Std_Dev, "CV_(%)_Testo_C",
                  Diff_Testo_B_A, Diff_Testo_C_B)) %>%
  gather(Cort, Testo, key = "hormone", value = "value") %>%
  separate(value, into = c("A_Conc", "A_Std", "A_CV", 
                           "B_Conc", "B_Std", "B_CV",
                           "C_Conc", "C_Std", "C_CV",
                           "Diff_B_A", "Diff_C_B"), sep = "_") %>%
  mutate(Diff = A_Conc) %>%
  unite("A", c("A_Conc", "A_Std", "A_CV", "Diff")) %>%
  unite("B", c("B_Conc", "B_Std", "B_CV", "Diff_B_A")) %>%
  unite("C", c("C_Conc", "C_Std", "C_CV", "Diff_C_B")) %>%
  gather(A,B,C,key = "session", value = "value") %>%
  separate(value, into = c("Conc", "Std", "CV", "Diff"), sep = "_", convert = T) %>%
  arrange(ID, hormone, session) %>%
  mutate(lag_Conc = lag(Conc)) %>%
  # create a percentage change
  mutate(per_diff = ifelse(session == "A",Diff,Diff/lag_Conc)) %>%
  filter(ID != "105C", ID != "113S", ID != "118C", ID != "146C", ID != "151C")
```

```{r, cache = TRUE, dependson = "tidying"}
# Create a dataframe unique for each hormone/ each condition

## Cortisol
Cort <- relation %>%
  filter(hormone == "Cort",!(is.na(Conc)))
Cort_control <- Cort %>%
  filter(tsst == "Control")

# Cortisol daaframe for comparing percentage change
Cort_per_diff <- Cort %>%
  select(-Conc,-Std,-CV,-Diff, -lag_Conc) %>%
  spread(session, value = per_diff) %>%
  arrange(ID)
Cort_per_diff_control <- Cort_per_diff %>%
  filter(tsst == "Control")

## Testosterone
Testo <- relation %>%
  filter(hormone == "Testo",!(is.na(Conc)))

Testo_F <- Testo %>%
  filter(gender == "Female")

Testo_F_control <- Testo_F %>%
  filter(tsst == "Control")

Testo_M <- Testo %>%
  filter(gender == "Male")

Testo_M_control <- Testo_M %>%
  filter(tsst == "Control")

# Testosterone dataframe for comparing percentage change
Testo_per_diff <- Testo %>%
  select(-Conc,-Std,-CV,-Diff, -lag_Conc) %>%
  spread(session, value = per_diff) %>%
  arrange(ID)

Testo_F_per_diff <- Testo_per_diff %>%
  filter(gender == "Female")

Testo_F_per_diff_control <- Testo_F_per_diff %>%
  filter(tsst == "Control")

Testo_M_per_diff <- Testo_per_diff %>%
  filter(gender == "Male")

Testo_M_per_diff_control <- Testo_M_per_diff %>%
  filter(tsst == "Control")
```

## C - A
### Cortisol
#### Control
* percentage change from baseline is not significant
    
```{r}
Cort_control %>%
  filter(session != "B") %>%
  plot_all()
  
t.test(Cort_per_diff_control$C)
```


#### All
* percentage change from baseline is not significant
  
```{r}
Cort%>%
  filter(session != "B") %>%
  plot_all()

t.test(Cort_per_diff$C)
```


### Testosterone Female
#### Control
* percentage change from baseline is not significant
    
```{r}
Testo_F_control %>%
  filter(session != "B") %>%
  plot_all()
  
t.test(Testo_F_per_diff_control$C)
```


#### All
* percentage change from baseline is not significant
  
```{r}
Testo_F%>%
  filter(session != "B") %>%
  plot_all()

t.test(Testo_F_per_diff$C)
```


### Testosterone Male
#### Control
* percentage change from baseline is not significant
    
```{r}
Testo_M_control %>%
  filter(session != "B") %>%
  plot_all()
  
t.test(Testo_M_per_diff_control$C)
```


#### All
* percentage change from baseline is not significant
  
```{r}
Testo_M %>%
  filter(session != "B") %>%
  plot_all()

t.test(Testo_M_per_diff$C)
```

## Tsst vs control
### Cortisol

```{r}
plot_repeated_meas(Cort) +
  labs(title = "Cortisol Concentration by Condition",
       y = "Cortisol Concentration")
```

```{r}
# Multiple linear regression
lm_c <- lm(data = Cort, Conc ~ session + tsst + session*tsst)
kable( tidy(lm_c) )
kable( glance(lm_c)[1:6] )
kable( anova(lm_c) )
```


### Testosterone
#### Female
```{r}
plot_repeated_meas(Testo_F)
```

```{r}
# Multiple linear regression
lm_t <- lm(data = Testo_F, Conc ~ session + tsst + session*tsst)
kable( tidy(lm_t) )
kable( glance(lm_t)[1:6] )
kable( anova(lm_t) )
```

#### Male
```{r}
plot_repeated_meas(Testo_M)
```

```{r}
# Multiple linear regression
lm_t <- lm(data = Testo_M, Conc ~ session + tsst + session*tsst)
kable( tidy(lm_t) )
kable( glance(lm_t)[1:6] )
kable( anova(lm_t) )
```