---
title: "EDA_correlation_basline"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
# global setting
knitr::opts_chunk$set(echo = F, warning = F, message = F)

# load libraries
library(tidyverse)
library(ggplot2)
library(ggpmisc)
library(rcompanion)
library(knitr)
library(broom)
library(data.table)
library(corrplot)
library(Hmisc)
# setting theme for ggplot
theme_set(theme_minimal())
theme_update(text = element_text(family = "Times"))
```

```{r}
## Load data
survey <- read_csv("data/survey_tidy.csv") %>%
  select(-X1, -Gender, -TSST)

Cort <- read_csv("data/Cortisol.csv") %>%
  inner_join(survey) %>%
  select(-number, -X1)

Testo_F <- read_csv("data/Testosterone_F.csv") %>%
  inner_join(survey) %>%
  select(-number, -X1)

Testo_M <- read_csv("data/Testosterone_M.csv") %>%
  inner_join(survey) %>%
  select(-number, -X1)

```


# Baseline
## Cortisol
### Condition before the experimental session
```{r}
res2 <- Cort %>%
  select(A_Conc, eat_drink, brush_before, sick_now, sick_past_wk, 
         is_worry_today, sleep_hrs_last_night, exercise)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Scales
* rMEQ
* sMARS
```{r}
res2 <- Cort %>%
  select(A_Conc, rMEQ_1_5, rMEQ_6, AQ, Anx_T, ACE, Lon, Mac_SS, sMARS)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic
```{r}
res2 <- Cort %>%
  select(A_Conc, age, Dem_Eth, Dem_Educ, Dem_Raised, Dem_Inc)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic (behavior)
```{r}
res2 <- Cort %>%
  select(A_Conc, Dem_Alc, Dem_Contra, Dem_Smoke, Dem_Subst)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic (relationship)
* Relationship Term (>6 mos)
* Relationship Stability
* Relationship Commitment
```{r}
res2 <- Cort %>%
  select(A_Conc, Dem_Marr, Dem_RelSta, Dem_RelTerm, Dem_RelLeng, Dem_RelDom, 
         Dem_RelStab, Dem_Commit, Dem_Marr_Length, Dem_Sexual_Activity) 

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Personality
```{r}
res2 <- Cort %>%
  select(A_Conc, BFI_E, BFI_A, BFI_C, BFI_N, BFI_O,
         TIPI_E, TIPI_A, TIPI_C, TIPI_ES, TIPI_O,
         TIPI_E_Post, TIPI_A_Post, TIPI_C_Post, TIPI_ES_Post, TIPI_O_Post)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Mating Orientation
```{r}
res2 <- Cort %>%
  select(A_Conc, STMO, LTMO, Future_STMO, Future_LTMO)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Mating Behavior
```{r}
res2 <- Cort %>%
  select(A_Conc, PSE_1:PSE_Fantas)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```


### STAI
```{r}
res2 <- Cort %>%
  select(A_Conc, STAI_S, STAI_S_Post)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

## Testosterone (M)
### Condition before the experimental session
* Eat/Drink
    
```{r}
res2 <- Testo_M %>%
  select(A_Conc, eat_drink, brush_before, sick_now, sick_past_wk, 
         is_worry_today, sleep_hrs_last_night, exercise)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Scales
```{r}
res2 <- Testo_M %>%
  select(A_Conc, rMEQ_1_5, rMEQ_6, AQ, Anx_T, ACE, Lon, Mac_SS, sMARS)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic
```{r}
res2 <- Testo_M %>%
  select(A_Conc, age, Dem_Eth, Dem_Educ, Dem_Raised, Dem_Inc)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic (behavior)
* Smoking
    
```{r}
res2 <- Testo_M %>%
  select(A_Conc, Dem_Alc, Dem_Smoke, Dem_Subst)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic (relationship)
```{r}
res2 <- Testo_M %>%
  select(A_Conc, Dem_Marr, Dem_RelSta, Dem_RelTerm, Dem_RelLeng, Dem_RelDom, 
         Dem_RelStab, Dem_Commit, Dem_Sexual_Activity) 

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Personality
```{r}
res2 <- Testo_M %>%
  select(A_Conc, BFI_E, BFI_A, BFI_C, BFI_N, BFI_O,
         TIPI_E, TIPI_A, TIPI_C, TIPI_ES, TIPI_O,
         TIPI_E_Post, TIPI_A_Post, TIPI_C_Post, TIPI_ES_Post, TIPI_O_Post)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Mating Orientation
* LTMO
    
```{r}
res2 <- Testo_M %>%
  select(A_Conc, STMO, LTMO, Future_STMO, Future_LTMO)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Mating Behavior
```{r}
res2 <- Testo_M %>%
  select(A_Conc, PSE_1:PSE_Fantas)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```


### STAI
```{r}
res2 <- Testo_M %>%
  select(A_Conc, STAI_S, STAI_S_Post)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

## Testosterone (F)
### Condition before the experimental session
* Eat/Drink
    
```{r}
res2 <- Testo_F %>%
  select(A_Conc, eat_drink, brush_before, sick_now, sick_past_wk, 
         is_worry_today, sleep_hrs_last_night, exercise)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Scales
```{r}
res2 <- Testo_F %>%
  select(A_Conc, rMEQ_1_5, rMEQ_6, AQ, Anx_T, ACE, Lon, Mac_SS, sMARS)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic
```{r}
res2 <- Testo_F %>%
  select(A_Conc, age, Dem_Eth, Dem_Educ, Dem_Raised, Dem_Inc)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic (behavior)
* Contraception
    
```{r}
res2 <- Testo_F %>%
  select(A_Conc, Dem_Alc, Dem_Contra, Dem_Smoke, Dem_Subst)

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Demographic (relationship)
```{r}
res2 <- Testo_F %>%
  select(A_Conc, Dem_Marr, Dem_RelSta, Dem_RelTerm, Dem_RelLeng, Dem_RelDom, 
         Dem_RelStab, Dem_Commit, Dem_Marr_Length, Dem_Sexual_Activity) 

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Personality
* BFI_C
* TIPI_O
    
```{r}
res2 <- Testo_F %>%
  select(A_Conc, BFI_E, BFI_A, BFI_C, BFI_N, BFI_O,
         TIPI_E, TIPI_A, TIPI_C, TIPI_ES, TIPI_O,
         TIPI_E_Post, TIPI_A_Post, TIPI_C_Post, TIPI_ES_Post, TIPI_O_Post)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Mating Orientation
```{r}
res2 <- Testo_F %>%
  select(A_Conc, STMO, LTMO, Future_STMO, Future_LTMO)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```

### Mating Behavior
```{r}
res2 <- Testo_F %>%
  select(A_Conc, PSE_1:PSE_Fantas)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```


### STAI
```{r}
res2 <- Testo_F %>%
  select(A_Conc, STAI_S, STAI_S_Post)

res2[is.na(res2)] <- 0

res2 <- rcorr(as.matrix(res2))
corrplot(res2$r, type="upper", order="original", 
         p.mat = res2$P, sig.level = 0.05, insig = "label_sig")
```