---
title: "EDA Survey"
output:
  github_document: 
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
# global setting
knitr::opts_chunk$set(echo = F, warning = F, message = F)

# load libraries
library(tidyverse)
library(ggplot2)
library(ggpmisc)
library(rcompanion)
library(knitr)
library(broom)
library(data.table)
# setting theme for ggplot
theme_set(theme_minimal())
theme_update(text = element_text(family = "Times"))
```

```{r,warning = FALSE, message = FALSE}
## load the data
survey <- read_csv("data/survey.csv") %>%
  select("Participant ID", Gender, "TSST/Control Condition", age, colorblind,
         rMEQ_1_5, rMEQ_6, AQ, Anx_T, ACE, Lon, Attractive_by_conf:reveal_detail_by_conf,
         eat_drink:Dem_Sexual_Activity, BFI_E, BFI_A, BFI_C, BFI_N, BFI_O,
         Mac_SS, TIPI_E, TIPI_A, TIPI_C, TIPI_ES, TIPI_O, sMARS, STMO, LTMO,
         Future_STMO, Future_LTMO, PSE_1:PSE_Fantas, STAI_S, STAI_S_Post, 
         TIPI_E_Post, TIPI_A_Post, TIPI_C_Post, TIPI_ES_Post, TIPI_O_Post,
         Imp_Attr:Imp_Like) %>%
  slice(2:157) %>%
  setnames(old=c("Participant ID","TSST/Control Condition"), new=c("ID", "TSST")) %>%
  filter(ID != "105C", ID != "113s", ID != "118C") %>%
  mutate_at(.vars = vars(age, rMEQ_6,Attractive_by_conf:is_worry_today, sleep_hrs_last_night,
                         exercise, Dem_Age, Dem_Gen, Dem_SO, Dem_Trans, Dem_Eth, Dem_Marr,
                         Dem_Educ,Dem_Raised, Dem_Smoke:Dem_Contra, Dem_Inc:Dem_Child,
                         Dem_RelDom:Imp_Like),
            .funs = as.numeric)

write.csv(survey, "survey_tidy.csv")
```

```{r}
sum_table <- function(var){
  rv <- summarise(survey,
                  n = n(),
                  mean = mean(var, na.rm = T),
                  sd = sd(var, na.rm = T),
                  min = min(var),
                  median = median(var),
                  max = max(var)
                  )
  return(rv)
}
```


## Demographic
### Age

```{r}
kable(sum_table(survey$age))
```

```{r}
ggplot(survey, aes(age)) +
    geom_dotplot(dotsize = 0.7)
```

### How many hours did you sleep last night?
```{r}
kable(sum_table(survey$sleep_hrs_last_night))
```

```{r}
ggplot(survey, aes(sleep_hrs_last_night)) +
    geom_dotplot(dotsize = 0.3)
```

### Ethnicity
```{r}
kable(summarise(group_by(survey, Dem_Eth), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Eth))) +
  geom_bar() +
  scale_x_discrete(labels = c("East Asian", "Indian", "Black/African American",
                   "Hispanic/Latino", "White", "Other")) +
  coord_flip()
```

### Maritial Status
```{r}
kable(summarise(group_by(survey, Dem_Marr), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Marr))) +
    geom_bar()+ 
  scale_x_discrete(labels = c("Never married", "Currently married", "Divorced")) +
  coord_flip()
```

### Education
```{r}
kable(summarise(group_by(survey, Dem_Educ), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Educ))) +
    geom_bar() +
  scale_x_discrete(labels = c("High School Graduate", "Some College", "College Graduate or Higher")) +
  coord_flip()
```

### Raised by
```{r}
kable(summarise(group_by(survey, Dem_Raised), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Raised))) +
    geom_bar() +
  scale_x_discrete(labels = c("A single parent","Two parents, married","Two parents, divorced","Grandparents/other relatives","Other")) +
  coord_flip()
```

### Household income
```{r}
kable(summarise(group_by(survey, Dem_Inc), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Inc))) +
    geom_bar() +
  scale_x_discrete(labels = c("<15,000", "15,000 - 30,000", "30,000 - 45,000",
                              "45,000 - 60,000", "60,000 - 75,000", "75,000 - 90,000",
                              "90,000 - 105,000", "105,000 - 120,000", "120,000 - 135,000",
                              "150,000 - 165,000", "165,000 - 180,000", "180,000 - 195,000",
                              ">195,000")) +
  coord_flip()
```

### Current Relationship Status
```{r}
kable(summarise(group_by(survey, Dem_RelSta), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_RelSta))) +
    geom_bar() +
  scale_x_discrete(labels = c("Single", "In a relationship (unmarried)", "Married")) +
  coord_flip()
```

### Current Relationship more than 6 months?
```{r}
kable(summarise(group_by(survey, Dem_RelTerm), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_RelTerm))) +
    geom_bar() +
  scale_x_discrete(labels = c("Yes","No")) +
  coord_flip()
```

### Current Relationship Commitment
```{r}
kable(summarise(group_by(survey, Dem_Commit), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Commit))) +
    geom_bar() +
  scale_x_discrete(labels = c("Yes","No")) +
  coord_flip()
```

### Current Relationship Length
```{r}
kable(sum_table(survey$Dem_RelLeng))
```

```{r}
ggplot(survey, aes(Dem_RelLeng)) +
    geom_dotplot(dotsize = 0.8)
```

### Current Marriage Length
```{r}
kable(sum_table(survey$Dem_Marr_Length))
```

### Do you have any children?
```{r}
kable(summarise(group_by(survey, Dem_Child), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_Child))) +
    geom_bar() +
  scale_x_discrete(labels = c("Yes","No")) +
  coord_flip()
```

### Who is dominant?
```{r}
kable(summarise(group_by(survey, Dem_RelDom), n = n()))
```

```{r}
ggplot(survey, aes(factor(Dem_RelDom))) +
    geom_bar() +
  scale_x_discrete(labels = c("I am definitely dominant", "I am somewhat dominant", "Neither", 
                              "My partner is somewhat dominant", "My partner is definitely dominant")) +
  coord_flip()
```

### Stable?
```{r}
kable(sum_table(survey$Dem_RelStab))
```

```{r}
ggplot(survey, aes(Dem_RelStab)) +
    geom_dotplot(dotsize = 0.3)
```

### Last sexual activity
```{r}
kable(summarise(group_by(survey, Dem_Sexual_Activity), n = n()))
```

```{r}
ggplot(survey, aes(Dem_Sexual_Activity)) +
    geom_bar() +
  scale_x_discrete(labels = c("Within last 24 hrs", "Within last week", "Within last month", "More than a month ago", "More than 6 months ago", "More than a year ago", "Have never engaged in sexual activity")) +
  coord_flip()
```

## Scales
### rMEQ
```{r}
kable(sum_table(survey$rMEQ_1_5))
```

```{r}
ggplot(survey, aes(rMEQ_1_5)) +
    geom_dotplot(dotsize = 0.7)
```

#### Average hours of sleep
```{r}
kable(sum_table(survey$rMEQ_6))
```

```{r}
ggplot(survey, aes(rMEQ_6)) +
    geom_dotplot(dotsize = 0.3)
```

### AQ
```{r}
kable(sum_table(survey$AQ))
```

```{r}
ggplot(survey, aes(AQ)) +
    geom_dotplot(dotsize = 0.7)
```

### Anx_T
```{r}
kable(sum_table(survey$Anx_T))
```

```{r}
ggplot(survey, aes(Anx_T)) +
    geom_dotplot(dotsize = 0.7)
```

### ACE
```{r}
kable(sum_table(survey$ACE))
```

```{r}
ggplot(survey, aes(ACE)) +
    geom_dotplot(dotsize = 0.3)
```

### Lon
```{r}
kable(sum_table(survey$Lon))
```

```{r}
ggplot(survey, aes(Lon)) +
    geom_dotplot(dotsize = 0.3)
```


### Mac_SS
```{r}
kable(sum_table(survey$Mac_SS))
```

```{r}
ggplot(survey, aes(Mac_SS)) +
    geom_dotplot(dotsize = 0.3)
```


### sMARS
```{r}
kable(sum_table(survey$sMARS))
```

```{r}
ggplot(survey, aes(sMARS)) +
    geom_dotplot(dotsize = 0.7)
```

### STAI (Pre)
```{r}
kable(sum_table(survey$STAI_S))
```

```{r}
ggplot(survey, aes(STAI_S)) +
    geom_dotplot(dotsize = 0.7)
```

### STAI (Post)
```{r}
kable(sum_table(survey$STAI_S_Post))
```

```{r}
ggplot(survey, aes(STAI_S_Post)) +
    geom_dotplot(dotsize = 0.7)
```

## Personality
### BFI
#### BFI_E
```{r}
kable(sum_table(survey$BFI_E))
```

```{r}
ggplot(survey, aes(BFI_E)) +
    geom_dotplot(dotsize = 0.7)
```

#### BFI_A
```{r}
kable(sum_table(survey$BFI_A))
```

```{r}
ggplot(survey, aes(BFI_A)) +
    geom_dotplot(dotsize = 0.7)
```

#### BFI_C
```{r}
kable(sum_table(survey$BFI_C))
```

```{r}
ggplot(survey, aes(BFI_C)) +
    geom_dotplot(dotsize = 0.7)
```

#### BFI_N
```{r}
kable(sum_table(survey$BFI_N))
```

```{r}
ggplot(survey, aes(BFI_N)) +
    geom_dotplot(dotsize = 0.7)
```

#### BFI_O
```{r}
kable(sum_table(survey$BFI_O))
```

```{r}
ggplot(survey, aes(BFI_O)) +
    geom_dotplot(dotsize = 0.7)
```


### TIPI (Pre)
#### TIPI_E
```{r}
kable(sum_table(survey$TIPI_E))
```

```{r}
ggplot(survey, aes(TIPI_E)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_A
```{r}
kable(sum_table(survey$TIPI_A))
```

```{r}
ggplot(survey, aes(TIPI_A)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_C
```{r}
kable(sum_table(survey$TIPI_C))
```

```{r}
ggplot(survey, aes(TIPI_C)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_ES
```{r}
kable(sum_table(survey$TIPI_ES))
```

```{r}
ggplot(survey, aes(TIPI_ES)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_O
```{r}
kable(sum_table(survey$TIPI_O))
```

```{r}
ggplot(survey, aes(TIPI_O)) +
    geom_dotplot(dotsize = 0.7)
```

### TIPI (Post)
#### TIPI_E
```{r}
kable(sum_table(survey$TIPI_E_Post))
```

```{r}
ggplot(survey, aes(TIPI_E_Post)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_A
```{r}
kable(sum_table(survey$TIPI_A_Post))
```

```{r}
ggplot(survey, aes(TIPI_A_Post)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_C
```{r}
kable(sum_table(survey$TIPI_C_Post))
```

```{r}
ggplot(survey, aes(TIPI_C_Post)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_ES
```{r}
kable(sum_table(survey$TIPI_ES_Post))
```

```{r}
ggplot(survey, aes(TIPI_ES_Post)) +
    geom_dotplot(dotsize = 0.7)
```

#### TIPI_O
```{r}
kable(sum_table(survey$TIPI_O_Post))
```

```{r}
ggplot(survey, aes(TIPI_O_Post)) +
    geom_dotplot(dotsize = 0.7)
```

## Mating
### STMO
```{r}
kable(sum_table(survey$STMO))
```

```{r}
ggplot(survey, aes(STMO)) +
    geom_dotplot(dotsize = 0.7)
```

### LTMO
```{r}
kable(sum_table(survey$LTMO))
```

```{r}
ggplot(survey, aes(LTMO)) +
    geom_dotplot(dotsize = 0.5)
```

### Future_STMO
```{r}
kable(sum_table(survey$Future_STMO))
```

```{r}
ggplot(survey, aes(Future_STMO)) +
    geom_dotplot(dotsize = 0.3)
```

### Future_LTMO
```{r}
kable(sum_table(survey$Future_LTMO))
```

```{r}
ggplot(survey, aes(Future_LTMO)) +
    geom_dotplot(dotsize = 0.1)
```

### Number of sexual partners
#### During your entire life, how many partners have you had sexual intercourse with?
```{r}
kable(sum_table(survey$PSE_1))
```

```{r}
ggplot(survey, aes(PSE_1)) +
    geom_dotplot(dotsize = 0.3)
```

#### Of these, how many could be characterized as brief sexual relationships?
```{r}
kable(sum_table(survey$PSE_1B))
```

```{r}
ggplot(survey, aes(PSE_1B)) +
    geom_dotplot(dotsize = 0.2)
```

#### How many of these involved high levels of commitment from your partner? 
```{r}
kable(sum_table(survey$PSE_1C))
```

```{r}
ggplot(survey, aes(PSE_1C)) +
    geom_dotplot(dotsize = 0.3)
```

#### How many were you highly committed to?
```{r}
kable(sum_table(survey$PSE_1D))
```

```{r}
ggplot(survey, aes(PSE_1D)) +
    geom_dotplot(dotsize = 0.3)
```

#### How many partners have you had sexual intercourse with in the past year?
```{r}
kable(sum_table(survey$PSE_2))
```

```{r}
ggplot(survey, aes(PSE_2)) +
    geom_dotplot(dotsize = 0.3)
```

#### Of these, how many could be characterized as brief sexual relationships?
```{r}
kable(sum_table(survey$PSE_2B))
```

```{r}
ggplot(survey, aes(PSE_2B)) +
    geom_dotplot(dotsize = 0.1)
```

#### How many of these involved high levels of commitment from your partner?
```{r}
kable(sum_table(survey$PSE_2C))
```

```{r}
ggplot(survey, aes(PSE_2C)) +
    geom_dotplot(dotsize = 0.3)
```

#### How many were you highly committed to?
```{r}
kable(sum_table(survey$PSE_2D))
```

```{r}
ggplot(survey, aes(PSE_2D)) +
    geom_dotplot(dotsize = 0.2)
```

#### During your entire life, how many partners have you had sexual intercourse with on one and only one occasion?
```{r}
kable(sum_table(survey$PSE_3))
```

```{r}
ggplot(survey, aes(PSE_3)) +
    geom_dotplot(dotsize = 0.2)
```

#### How many partners do you foresee having sexual intercourse with during the next five years? 
```{r}
kable(sum_table(survey$PSE_Future))
```

```{r}
ggplot(survey, aes(PSE_Future)) +
    geom_dotplot(dotsize = 0.3)
```

#### With how many of these partners do you foresee having a long-term, committed (as defined above) sexual relationship?
```{r}
kable(sum_table(survey$PSE_FutureB))
```

```{r}
ggplot(survey, aes(PSE_FutureB)) +
    geom_dotplot(dotsize = 0.2)
```

#### With how many of these partners do you foresee yourself having a short-term, uncommitted sexual relationship?
```{r}
kable(sum_table(survey$PSE_FutureC))
```

```{r}
ggplot(survey, aes(PSE_FutureC)) +
    geom_dotplot(dotsize = 0.1)
```

#### How often do you fantasize about having sex with someone other than your current dating partner / spouse?
```{r}
kable(sum_table(survey$PSE_Fantas))
```

```{r}
ggplot(survey, aes(PSE_Fantas)) +
    geom_dotplot(dotsize = 0.3)
```